---
title: "ASPECT — Figures"
format: html
toc: true
---

```{r setup, include=FALSE}
# Load all data from analysis script
load("results/analysis_workspace.RData")

library(tidyverse)
library(janitor)
library(ggplot2)
library(ggpubr)
library(patchwork)
library(viridis)
library(pheatmap)
library(survival)
library(survminer)
library(forestmodel)
library(mlr3)
library(mlr3learners)
library(mlr3viz)
library(ranger)

knitr::opts_chunk$set(fig.width=10, fig.height=6, warning=FALSE, message=FALSE)
```

::: {.callout-important}
**Prerequisite:** Run `scripts/6_analysis.R` first.
:::

### Auc Plot

```{r}
auc_plot <- ggplot(plot_data_sorted_auc, aes(x = drug_name, y = auc, fill = model_name)) +
  geom_col(position = position_dodge(width = 0.9)) +
  labs(
    title = "Comparison of Drug Predictive AUC across Models",
    subtitle = "Grouped by Drug",
    x = "Drug Name",
    y = "AUC",
    fill = "Model"  # This is the legend title
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # Rotate when x-axis labels are too long
```

### Figure 2

```{r}
print(auc_plot)
ggsave('/Users/hechang/Documents/chenlab/fig/auc_plot_reversed.png',auc_plot)
```

### Recall Plot

```{r}
recall_plot <- ggplot(plot_data_sorted_recall, aes(x = drug_name, y =recall_top_n, fill = model_name)) +
  geom_col(position = position_dodge(width = 0.9)) +
  labs(
    title = "Comparison of Drug Recall @ Top-N across Models",
    subtitle = "Grouped by Drug",
    x = "Drug Name",
    y = "Recall @ Top-N",
    fill = "Model" # Legend title
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Figure 4

```{r}
print(recall_plot)
ggsave('/Users/hechang/Documents/chenlab/fig/recall_plot_reversed.png',recall_plot)
```

### Figure 5

```{r}
ggplot(plot_data, aes(x = Group, y = Prop, fill =Status)) +
  geom_col(position = "fill") +
  labs(title = "Proportion of Metastatic Samples", y = "Proportion") +
  theme_minimal()
```

### Figure 6

```{r}
ggplot(viz_data, aes(x = CancerType, y = OncotreeLineage)) +
  # Draw bubbles
```

### Figure 7

```{r}
ggplot(plot_data, aes(x = Purity_Group, y = Predicted_IC50, fill = Purity_Group)) +
  geom_boxplot(outlier.alpha = 0.3) +
  # Add P-value comparison (Low vs High)
  stat_compare_means(comparisons = list(c("Low", "High")),
```

### Figure 8

```{r}
ggplot(plot_data_subset, aes(x = TumorPurity, y = Predicted_IC50)) +
  # 1. Scatter points
```

### Figure 9

```{r}
ggplot(brca_data, aes(x = Subtype, y = Predicted_IC50, fill = Subtype)) +
  # 1. Boxplot + jitter
```

### Figure 10

```{r}
ggplot(ov_data, aes(x = Subtype, y = Predicted_IC50, fill = Subtype)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.2, size = 1) +
```

### Figure 11

```{r}
ggplot(skcm_data, aes(x = Subtype_Label, y = Predicted_IC50, fill = Subtype_Label)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.7) +
  geom_jitter(width = 0.2, alpha = 0.2) +
  scale_fill_brewer(palette = "YlOrRd") + # Gradient color
```

### Figure 12

```{r}
ggplot(prad_data, aes(x = Group, y = Predicted_IC50, fill = Group)) +
  geom_boxplot(alpha = 0.7) +
  stat_compare_means(method = "wilcox.test") +
  labs(
    title = "Validation in Prostate Cancer (PRAD)",
    subtitle = "ERG Fusion status check",
    x = "Subtype Group",
    y = "Predicted Score (IC50)"
  ) +
  theme_bw()
```

### P

```{r}
p <- ggplot(plot_data, aes(x = Subtype, y = CBI, fill = Subtype)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.8) +
    geom_jitter(width = 0.2, alpha = 0.1, size = 0.8) +
```

### Figure 14

```{r}
print(p1)
```

### Figure 15

```{r}
print(p2)
```

### Figure 16

```{r}
print(p3)
```

### Figure 17

```{r}
print(p4)
```

### Figure 18

```{r}
(p1 | p2) / (p3 | p4)
```

### P Immune

```{r}
p_immune <- ggplot(brca_est_merged, aes(x = Subtype, y = ImmuneScore, fill = Subtype)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.8) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 0.5) +
```

### P Purity

```{r}
p_purity <- ggplot(brca_est_merged, aes(x = Subtype, y = TumorPurity, fill = Subtype)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.8) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 0.5) +
  stat_compare_means(comparisons = list(c("Other", "Basal")),
```

### Figure 21

```{r}
print(combined_plot)
```

### Figure 22

```{r}
ggplot(plot_ccle_ic50_dist, aes(x = Status, y = IC50, fill = Status)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.8) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 0.5) +
  stat_compare_means(comparisons = list(c('Metastatic', 'Primary')),label = "p.signif", size=5) +
```

### Figure 23

```{r}
autoplot(bmr, measure = msr("classif.acc")) +
```

### Figure 24

```{r}
ggplot(cm_df, aes(x = True_Class, y = Predicted_Class, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = Freq), color = "black", size = 5) +
  scale_fill_gradient(low = "#F0F0F0", high = "#DC143C") +
  labs(
    title = "Confusion Matrix: Comb Model",
    x = "Actual Clinical Subtype",
    y = "Predicted Subtype"
  ) +
  theme_minimal() +
  theme(
    axis.text = element_text(size = 10),
    plot.title = element_text(face = "bold")
  )
```

### Figure 25

```{r}
ggplot(top_features, aes(x = reorder(Feature, Importance), y = Importance)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(
    title = "Top predictive features",
    x = "Drug Name",
    y = "Importance (Gini Impurity)"
  ) +
  theme_classic()
```

### Figure 26

```{r}
print(p_lgg)
```

### Figure 27

```{r}
print(p_brca)
```

### Figure 28

```{r}
print(p_skcm)
```

### Figure 29

```{r}
print(forest_lgg)
```

### Figure 30

```{r}
print(forest_brca)
```

### P Boxplot

```{r}
p_boxplot <- ggplot(lgg_master_data, aes(x = Subtype_DNAmeth, y = CBI, fill = Subtype_DNAmeth)) +
  geom_boxplot(outlier.shape = NA, alpha = 0.8, width = 0.6) +
  geom_jitter(width = 0.2, alpha = 0.3, size = 1) +
```

### Figure 32

```{r}
print(p_boxplot)
```

### P Corr

```{r}
p_corr <- ggplot(lgg_master_data, aes(x = TOP2A, y = CBI)) +
  # Color by subtype to visualize distribution clusters
```

### Figure 34

```{r}
print(p_corr)
```

### P Corr Faceted

```{r}
p_corr_faceted <- ggplot(lgg_master_data, aes(x = TOP2A, y = CBI)) +
  # 1. Scatter points: colored by subtype for clarity
```

### Figure 36

```{r}
print(p_corr_faceted)
```

### P

```{r}
p <- ggplot(plot_dat, aes(x = .data[[info$Drug1]], y = .data[[info$Drug2]])) +
      geom_point(alpha = 0.4, color = "#2E8B57", size = 1.5) +
      geom_smooth(method = "lm", color = "black", linetype = "dashed", se = TRUE) +
```

### Figure 38

```{r}
print(final_panel_a)
```

### Panel B

```{r}
panel_b <- ggplot(waterfall_data, aes(x = SampleID, y = Z_Score, fill = DrugName)) +
  geom_col(position = "stack", width = 1) + # Stacked bar chart
```

### Figure 40

```{r}
print(panel_b)
```

### Figure 41

```{r}
pheatmap(
  scale = "column",
  spec_mat,
  color = colorRampPalette(c("navy", "white", "firebrick"))(100),
  cluster_rows = TRUE,
  cluster_cols = TRUE,
  main = "Panel C: Regimen Specificity (Mean Predicted Sensitivity)",
  fontsize_row = 8,
  fontsize_col = 9,
  angle_col = 45
)
```

### P Refined

```{r}
p_refined <- ggplot(overlap_df_refined, aes(x = Drug1, y = Drug2)) +
  # 1. Grid background
```

### Figure 43

```{r}
print(p_refined)
```

### Figure 44

```{r}
ggplot(plot_data_novel, aes(x = Log2OR, y = -log10(P_Value))) +
  # 1. Background points (NS and Known)
  geom_point(data = subset(plot_data_novel, !grepl("Novel", Category)),
```

### P

```{r}
p <- ggplot(data, aes(x = CellType, y = CBI, fill = CellType)) +
    geom_boxplot(outlier.shape = NA, alpha = 0.8) +
    geom_jitter(width = 0.2, alpha = 0.4, size = 1.5) +
    stat_compare_means(label.y = max(data$CBI) * 1.1) +
    scale_fill_viridis_d(option = "turbo") +
    labs(
      title = paste0("Mechanism Validation: ", title_suffix),
      x = "Cell Type", y = "Score"
    ) +
    theme_classic() +
    theme(
      axis.text.x = element_text(angle = 45, hjust = 1, face = "bold"),
      legend.position = "none"
    )
```

### P

```{r}
p <- ggplot(plot_data, aes(x = Group, y = CBI, fill = Group)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA) +
    geom_point(aes(group = Patient), size = 2, alpha = 0.6) +
    #geom_line(aes(group = Patient), color = "grey50", alpha = 0.5) +
    facet_wrap(~CellType, scales = "free_y") +
    #stat_compare_means(method = "t.test", paired = TRUE, label = "p.format", label.x.npc = "center") +
    scale_fill_manual(values = c("Pre-treatment" = "#DC143C", "Post-treatment" = "#4682B4")) +
    labs(title = paste0("Pre vs Post: ", title_suffix), y = "Score") +
    theme_bw() + theme(legend.position = "none", axis.title.x = element_blank())
```

### P

```{r}
p <- ggplot(plot_data, aes(x = Outcome, y = CBI, fill = Outcome)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA) +
    geom_jitter(width = 0.2, size = 2, alpha = 0.6) +
    facet_wrap(~CellType, scales = "free_y") +
    #stat_compare_means(method = "t.test", label = "p.signif", label.x.npc = "center") +
    scale_fill_manual(values = c("Sensitive" = "#2E8B57", "Resistant" = "#B22222")) +
    labs(title = paste0("Baseline Prediction: ", title_suffix), y = "Pre-treatment Score") +
    theme_bw() + theme(legend.position = "none", axis.title.x = element_blank())
```

### Figure 48

```{r}
print(p2_tissue)
```

### Figure 49

```{r}
print(p1_blood)
print(p2_blood)
print(p3_blood)
```

### Figure 50

```{r}
ggplot(plot_data_box, aes(x = CBI_Group, y = M2_Score, fill = CBI_Group)) +
```

### P D New

```{r}
p_d_new <- ggplot(clean_data, aes(x = CBI, y = Expr)) +
    geom_point(aes(color = Status), size = 3, alpha = 0.7) +
    geom_smooth(method = "lm", color = "black", linetype = "dashed") +
    stat_cor(method = "spearman", label.x.npc = "left") +
    scale_color_manual(values = c("Pre" = "#DC143C", "Post" = "#4682B4", "Prog" = "black")) +
    labs(
      x = "TAMs Response Score",
      y = paste0(target_gene, " Expression (Z-Score)")
    ) +
    theme_classic()
```

### Figure 52

```{r}
plot_layout(guides = "collect") + # <--- Collect all legends into one place
```

### Figure 53

```{r}
print(combined_plot)
```

